TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-09-20 paper/draft.tex
model assumptions

\thecannon\ is a fully empirical model, which applies no use of line lists or radiative transfer models. Describe the assumptions of the model: (1) Sources with identical labels have near-identical flux at each pixel; (2) Expected flux at each pixel varies continuosly with change in label.

>>>>

\thecannon\ is a fully empirical model, which employs no use of line lists or radiative transfer models. Instead, \thecannon\ is a regression model which relies on two assumptions: first that sources with identical labels have near-identical flux at each pixel, and second that the expected flux at each pixel varies continuosly with change in label.
